The \dealii Library, Version 9.0

### 2018-04-28 9.0/paper.tex
Write about AVX-512.
Fix part on transfinite interpolation manifold.

There are also numerous improvements to the available manifold descriptions.
First, the manifold smoothing algorithms applied in the \texttt{Triangulation} class and
\texttt{MappingQGeneric} have been changed from the old Laplace-style smoothing to a
transfinite interpolation that linearly blends between the descriptions on the
faces around a cell. The old transformation introduced boundary layers inside
cells that prevented convergence rates from exceeding \(3.5\) in the global
\(L^2\) errors for typical settings. This change also considerably improves mesh
quality in situations where curved descriptions are only applied to the boundary
rather than the whole volume.

\marginpar{This paragraph seems to duplicate the previous. Can we
  merge the information?}
Secondly, a new manifold class
\texttt{TransfiniteInterpolationManifold} has been added that implements an
interpolation from a curved boundary description to the interior.
This class enables high-order convergence rates of better than ${\cal O}(h^3)$
for situations where a curved manifold can only be prescribed
to the boundary but not in a whole volume.

@@

The matrix-free infrastructure in \dealii{} was significantly overhauled for
the current release. The major new contribution is the support of face
integrals through a new class \texttt{FEFaceEvaluation}. The new class has a
similar interface as the existing \texttt{FEEvaluation} class, and applies SIMD
vectorization over several faces in analogy to the intra-cell vectorization in
FEEvaluation. Discontinuous Galerkin operators are implemented defining two
face functions, one for interior and one for boundary faces, in addition to
the cell function. These kernels for the matrix-free operator evaluation are
now collected in the new function \texttt{MatrixFree::loop}. The data
structures have been particularly tuned for typical discontinuous Galerkin
setups involving operators with first and second spatial derivatives. Both
data access and computations have been thoroughly optimized and compared to
the performance boundaries of the hardware.

>>>>

There are also numerous improvements to the available manifold descriptions.
First, the manifold smoothing algorithms applied in the \texttt{Triangulation} class and
\texttt{MappingQGeneric} have been changed from the old Laplace-style smoothing to a
transfinite interpolation that linearly blends between the descriptions on the
faces around a cell. The old transformation introduced boundary layers inside
cells that prevented convergence rates from exceeding \(3.5\) in the global
\(L^2\) errors for typical settings. This change also considerably improves mesh
quality in situations where curved descriptions are only applied to the boundary
rather than the whole volume. This concept was also introduced as a new manifold class
\texttt{TransfiniteInterpolationManifold}, which allows to apply this type of smoothing not only in the cells close to the boundary but over a full coarse (level 0) cell.

@@

The matrix-free infrastructure in \dealii{} was significantly overhauled for
the current release. The major new contribution is the support of face
integrals through a new class \texttt{FEFaceEvaluation}. The new class has a
similar interface as the existing \texttt{FEEvaluation} class, and applies SIMD
vectorization over several faces in analogy to the intra-cell vectorization in
FEEvaluation. Discontinuous Galerkin operators are implemented defining two
face functions, one for interior and one for boundary faces, in addition to
the cell function. These kernels for the matrix-free operator evaluation are
now collected in the new function \texttt{MatrixFree::loop}. The data
structures have been particularly tuned for typical discontinuous Galerkin
setups involving operators with first and second spatial derivatives. Both
data access and computations have been thoroughly optimized and compared to
the performance boundaries of the hardware. Furthermore, the support for
AVX-512 instructions in the matrix-free framework was extended, adding new
\texttt{gather} and \texttt{scatter} intrinsics for the indirect access to
vector entries where appropriate.
